Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core

### 2006-08-20 BD_radvel/mn060888mj_rev/kurosawa.tex
Finished my revision (RK).
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@787 25464f21-6099-402c-b30a-640f1d40d38b

The data were reduced via the standard ESO pipeline procedures for
UVES echelle spectra. In summary, the data were corrected for bias,
interorder background, sky background, sky emission lines and cosmic
ray hits. They were then flattened, optimally extracted, and finally
the different orders were merged. No binning was performed to achieve
high resolution required for the RV measurements. The wavelength was
calibrated using the Thorium-Argon arc spectra with a typical value
of the standard deviation of the dispersion solution of 5~m\AA\,
which corresponds to 0.2~$\kmps$ at the central wavelength 8600~\AA.
However, the autoguiding of the telescope keeps the star at the centre
of the slit with about a tenth of the FWHM ($1\,\kmps$) which sets
the upper limit for the systematic error in the RV measurements
\citep{bailer-jones:2004}.
\textcolor{red}{
As we will find out in the following section
(Section~\ref{sub:Radial-velocities}), the systematic error may be
ignored based on result of the $\chi^{2}$ probability analysis we
performed without the introduction of assumed systematic error.
}
A typical
signal-to-noise ratio (S/N) per wavelength bin of the spectra is about
15, and the heliocentric velocity correction was applied to the final
spectra.

\begin{table*}

@@

@@

\caption{Summary of the observations, the heliocentric radial velocities ($\mathrm{RV}$)
from two-epoch and the average rotational velocities ($v\sin i$).
The uncertainties of relative radial velocities ($\sigma_{\mathrm{RRV}}$)
with respect to the template star LHS~049 and the average radial
velocities ($\overline{\mathrm{RV}}$) are also given.  
\textcolor{red}{
N.B.~the uncertainties listed along with the heliocentric radial
velocities in column~4 and 6 includes the uncertainty in the
heliocentric RV of the template star, but $\sigma_{\mathrm{RRV}}$
do not.
}
}

@@

Before applying the cross-correlation technique to our main targets,
we have applied the technique to the radial velocity standard
HD~140538 \textcolor{red}{(G2.5V)}
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed \'{e}celle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric 
\textcolor{red}{
$\mathrm{RV_{HD\,140538}=}19.17\pm0.40\,\kmps$
}
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.
\textcolor{red}{
  Note that the uncertainty in $\mathrm{RV_{HD\,140538}}$ was computed
  by combining the uncertainty ($0.4~\kmps$) in the heliocentric RV of
  the template star HD~74497 (G3V) and the uncertainty in the
  relative RV of HD~140538 ($0.02~\kmps$), measured with respect to
  the template star.  Clearly, the former dominates in the uncertainty
  in the value of $\mathrm{RV_{HD\,140538}}$ shown above. The
  uncertainty in the heliocentric RV of the template is rather large
  since it was determined from a few photospheric lines.
}

\textcolor{red}{
  The result of the heliocentric RV measurements (from two
  epochs for each object) is summarised in Table 2 along with their
  uncertainties.  The uncertainties listed with the
  absolute/heliocentric RV values in the 4-th and 6-th columns in the
  table include the uncertainty of the absolute/heliocentric RV of
  the template star. On the other hand, the uncertainties in the
  `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) listed in the 5-th
  column do not include the uncertainty of the template star. It is
  $\sigma_{\mathrm{RRV}}$ that is relevant for the identification of RV variable
  objects.  
}

To determine the $\sigma_{\mathrm{RRV}}$, we have used the following
procedure: (1)~add random gaussian deviate noise to the object spectra using the
corresponding variance spectra\footnote{\textcolor{red}{Defined by the variance of the
chi-square fit to the signal obtained during optimum extraction.}}, 
(2)~compute the cross-correlation
curve using the spectra with added noise and the template, (3)~measure
the RV by locating the peak, (4)~repeat 1--3 for 100 times, and compute the standard
deviation of the 100 RV values. This should provide a good estimate of
uncertainties in RVs cased by the uncertainties in the flux levels.
We also estimated the RV uncertainties using the standard deviations on the
mean of the two independent RV measurements obtained from the two
consecutive spectra taken on the same night (c.f.~\citealt{joergens:2006}).
We found that these estimates agreed well with those obtained from
the Monte Carlo method. The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
two epochs are also given in Table~\ref{tab:summary_results}.

@@

We have computed $p$ for all the objects (Table~\ref{tab:chisq_prob}),
and have plotted the results  
as a histogram of $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
(excluding the non-member USco~121; see explanation later). 
The figure clearly shows two distinctive populations: one on the left
(with small $-\log{p}$ values) occupied by the RV constant objects,
and one on the right (with the large $-\log{p}$ values)
occupied by the RV variable candidates.  The
expected distribution of $p$ computed consistently with our
uncertainty measurements is also shown in the same figure. The RV
constant population on the left side reasonably matches the expected
curve. 
\textcolor{red}{
To quantify this point, we have computed the
$\chi^{2}$ probability to test the goodness of the fit of the expected
distribution to the histogram. We restrict the fit to the first 4 bins
from the left $\left(0 < -\log_{10}p < 2 \right)$ the
histogram since the objects in the second bin from the right
$\left(2.5 < -\log_{10}p < 3 \right)$ are `potentially'
RV-variable object, although we have flagged them as the RV-constant
objects. In this analysis, we find the probability of 0.5 which
indicates that the fit is reasonable. Further, if we re-normalized the
expected distribution, accounting for that fact we neglected the
objects in the second bin from the right, we find the $\chi^{2}$
probability of the fit increases to 0.9.  This, in turn, indicates
that our uncertainties in RV values are reasonable, and an additional
systematic error may not be necessary in this analysis. 
}

\textcolor{red}{
There are two possible
source of systematic errors: (1)~the RV shifts caused by surface/atmospheric
activity, and (2)~the RV shifts due to the limit of the stability of
autoguiding of the telescope.  \citet{joergens:2006} found that (1) is
negligibly small for young VLM objects with $M_{*}<0.12\,M_{\sun}$.
The size of RV errors caused by (2) is expected to be $<1\,\kmps$
\citep{bailer-jones:2004}. Note that \citet{maxted:2005} found an
additional systematic error was not needed to be added to the RV
uncertainties of \citet{joergens:2006} who used the same instruments
as ours, and used the same method of estimating the
uncertainties.
}

@@

Follow-up spectroscopic observations of the binary candidates
presented here are planned in near future. There are only a few RV
variable binary candidates identified in earlier surveys
(\citealt{guenther:2003}; \citealt{kenyon:2005}; \citealt{joergens:2006}).
As \citet{burgasser:2006} points out most of the current RV and
imaging surveys use samples from magnitude-limited survey, but one
should attempt to use the samples from volume-limited survey in order
to find a correct statistics on binary parameters more straightforwardly,
i.e. without correcting for bias. 
\textcolor{red}{
Finally, we note that the binary fraction found in this paper may be
over-estimated because of the nature of our survey (magnitude-limited
and incomplete), hence because of a possible bias towards the brighter
objects.
}

@@

>>>>

@@

The data were reduced via the standard ESO pipeline procedures for
UVES echelle spectra. In summary, the data were corrected for bias,
interorder background, sky background, sky emission lines and cosmic
ray hits. They were then flattened, optimally extracted, and finally
the different orders were merged. No binning was performed to achieve
high resolution required for the RV measurements. The wavelength was
calibrated using the Thorium-Argon arc spectra with a typical value
of the standard deviation of the dispersion solution of 5~m\AA\,
which corresponds to 0.2~$\kmps$ at the central wavelength 8600~\AA.
However, the autoguiding of the telescope keeps the star at the centre
of the slit with about a tenth of the FWHM ($1\,\kmps$) which sets
the upper limit for the systematic error in the RV measurements
\citep{bailer-jones:2004}.
\textcolor{red}{
As we will find out in the following section
(Section~\ref{sub:Radial-velocities}), the systematic error may be
ignored based on the result of the $\chi^{2}$ probability analysis we
performed without the introduction of an assumed systematic error.
}
A typical
signal-to-noise ratio (S/N) per wavelength bin of the spectra is about
15, and the heliocentric velocity correction was applied to the final
spectra.

@@

\caption{Summary of the observations, the heliocentric radial velocities ($\mathrm{RV}$)
from two-epoch and the average rotational velocities ($v\sin i$).
The uncertainties of relative radial velocities ($\sigma_{\mathrm{RRV}}$)
with respect to the template star LHS~049 and the average radial
velocities ($\overline{\mathrm{RV}}$) are also given.  
\textcolor{red}{
N.B.~the uncertainties listed along with the heliocentric radial
velocities in column~4 and 6 include the uncertainty in the
heliocentric RV of the template star, but $\sigma_{\mathrm{RRV}}$ in
column~5 do not.
}
}

@@

Before applying the cross-correlation technique to our main targets,
we have applied the technique to the radial velocity standard
HD~140538 \textcolor{red}{(G2.5V)}
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed \'{e}celle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric 
\textcolor{red}{
$\mathrm{RV_{HD\,140538}=}19.17\pm0.40\,\kmps$
}
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.
\textcolor{red}{
  Note that the uncertainty in $\mathrm{RV_{HD\,140538}}$ was computed
  by combining the uncertainty ($0.4~\kmps$) in the heliocentric RV of
  the template star HD~74497 (G3V) and the uncertainty in the
  relative RV of HD~140538 ($0.02~\kmps$), measured with respect to
  the template star.  Clearly, the former dominates in the uncertainty
  in the value of $\mathrm{RV_{HD\,140538}}$ shown above. The
  uncertainty in the heliocentric RV of the template is rather large
  because it was determined from a few photospheric lines.
}

\textcolor{red}{
  The result of the heliocentric RV measurements (from two epochs for
  each object) is summarised in Table 2 along with their
  uncertainties.  The uncertainties listed in columns~4 and 6 along
  with the absolute/heliocentric RV values include the uncertainty of
  the absolute/heliocentric RV of the template star. On the other
  hand, the uncertainties in the `relative' radial velocities
  ($\sigma_{\mathrm{RRV}}$) listed in column~5 of the table do not
  include the uncertainty of the template star. It is
  $\sigma_{\mathrm{RRV}}$ that is relevant for the identification of
  RV variable objects.
}

To determine the $\sigma_{\mathrm{RRV}}$, we have used the following
procedure: (1)~add random gaussian deviate noise to the object spectra using the
corresponding variance spectra\footnote{\textcolor{red}{Defined by the variance of the
$\chi^{2}$ fit to the signal obtained during optimum extraction \citep[c.f.][]{horne:1986}.}}, 
(2)~compute the cross-correlation
curve using the spectra with added noise and the template, (3)~measure
the RV by locating the peak, (4)~repeat 1--3 for 100 times, and compute the standard
deviation of the 100 RV values. This should provide a good estimate of
uncertainties in RVs cased by the uncertainties in the flux levels.
We also estimated the RV uncertainties using the standard deviations on the
mean of the two independent RV measurements obtained from the two
consecutive spectra taken on the same night (c.f.~\citealt{joergens:2006}).
We found that these estimates agreed well with those obtained from
the Monte Carlo method. The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
two epochs are also given in Table~\ref{tab:summary_results}.

@@

We have computed $p$ for all the objects (Table~\ref{tab:chisq_prob}),
and have plotted the results  
as a histogram of $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
(excluding the non-member USco~121; see explanation later). 
The figure clearly shows two distinctive populations: one on the left
(with small $-\log{p}$ values) occupied by the RV constant objects,
and one on the right (with the large $-\log{p}$ values)
occupied by the RV variable candidates.  The
expected distribution of $p$ computed consistently with our
uncertainty measurements is also shown in the same figure. The RV
constant population on the left side reasonably matches the expected
curve. 
\textcolor{red}{
To quantify this point, we compute the
$\chi^{2}$ probability to test the goodness of the fit of the expected
distribution to the histogram. We restrict the fit to the first 4 bins
from the left $\left(0 < -\log_{10}p < 2 \right)$ of the
histogram since the objects in the second bin from the right
$\left(2.5 < -\log_{10}p < 3 \right)$ are `potentially'
RV-variable, although we have flagged them as the RV-constant
objects. In this analysis, we find the probability of 0.5 which
indicates that the fit is reasonable. Further, if we re-normalized the
expected distribution, accounting for that fact we neglected the
objects in the second bin from the right, we find the $\chi^{2}$
probability of the fit increases to 0.9.  This, in turn, indicates
that our uncertainties in RV values are reasonable, and an additional
systematic error may not be necessary in this analysis. 
}

\textcolor{red}{
There are two possible
sources of systematic errors: (1)~the RV shifts caused by surface/atmospheric
activity, and (2)~the RV shifts due to the limit of the stability of
autoguiding of the telescope.  \citet{joergens:2006} found that (1) is
negligibly small for young VLM objects with $M_{*}<0.12\,M_{\sun}$.
The size of RV errors caused by (2) is expected to be $<1\,\kmps$
\citep{bailer-jones:2004}. Note that \citet{maxted:2005} found an
additional systematic error was not needed to be added to the RV
uncertainties of \citet{joergens:2006} who used the same instruments
as ours, and used the same method of estimating the
uncertainties.
}

@@

Follow-up spectroscopic observations of the binary candidates
presented here are planned in near future. There are only a few RV
variable binary candidates identified in earlier surveys
(\citealt{guenther:2003}; \citealt{kenyon:2005}; \citealt{joergens:2006}).
As \citet{burgasser:2006} points out most of the current RV and
imaging surveys use samples from magnitude-limited survey, but one
should attempt to use the samples from volume-limited survey in order
to find a correct statistics on binary parameters more straightforwardly,
i.e. without correcting for bias. 
\textcolor{red}{
Finally, we note that the binary fraction found in this paper may be
over-estimated because of the nature of our survey (magnitude-limited
and incomplete), and because of a possible bias towards brighter
objects.
}

@@

\bibitem[{{Horne}(1986)}]{horne:1986}
{Horne} K., 1986, \pasp, 98, 609
